Plant-pollintor networks worldwide are composed by the same specific building

### 2021-05-27 Draft/Draft.Rmd
some more edits

We have compiled 60 plant-pollinator networks from 18 different studies (Table S1). All studies sampled plant-pollinator interactions in natural systems and were selected based on wide geographical coverage and the presence of interaction frequency as a measure of interaction strength. In total, there were 503 plant species, 1111 pollinator species and 6248 of plant-pollinator interactions counted. For ease of data manipulation plant and pollinator species names were standardize with the help of the package taxize version 0.9.99 [@chamberlain2020].

@@

>>>>

**Plant-pollinator studies**

We have compiled 60 plant-pollinator networks from 18 different studies (Table S1). All studies sampled plant-pollinator interactions in natural systems and were selected based on wide geographical coverage and the presence of interaction frequency as a measure of interaction strength. In total, there were 503 plant species, 1111 pollinator species and 6248 of pairwise interactions registered. For ease of data manipulation plant and pollinator species names were standardize with the help of the package taxize version 0.9.99 [@chamberlain2020].

**Plant functional groups and pollinator guilds**

First, we grouped plant species into five functional groups that summarized the main plant reproductive strategies. This was done with the help of the plant trait dataset built in Lanuza et al., (unpublished) that consisted of 16 plant functional traits (x floral, x reproductive and x vegetative; Table S2).

Second,...

This dataset had 16 traits

The high number of plant orders in this dataset (38) makes difficult to summarize plants on functional groups

reproductive strategies with the help of hierarchical clustering analysis. This was done by using a dataset compiled on the same set of networks that had 16

@@

Functional groups
We calculated the distance of the different functional traits with the function gowdis from the package FD (Laliberté et al., 2014) with the method ward.D2 used for non-squared distances (Murtagh & Legendre, 2014). All the numerical traits were previously scaled. Then, we applied  a hierarchical cluster analysis with the function hclust from the R stats package and we found the optimal number of clusters with the function kgs that conducts the penalty function of Kelley et al., (1996) from the package maptree (White & Gramacy, 2009).
